---
title: "1-Quadratic Voting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1-Quadratic Voting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.showtext = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(VulnerabilityScoreCalibration)
```

# Facilitation with Quadratic Voting
A quick tutorial to use quadratic voting using a survey platform (xlsform based like kobotoolobox or ODK...).

> Quadratic voting is an innovative approach for collective and inclusive decision making. .


## Enabling collective decision-making with quadratic voting.

Making strategic decisions in a collective and inclusive way is challenging. In the absence of a clear facilitation approach to deal with diverging views, adverse effects are likely to occurs and can lead to poor programmatic effectiveness. At different stage of programme management process, (i.e. Situation Analysis, Strategic Prioritization & Resource's allocation) decisions might:

-   Be led by the offer (i.e., proposal from partners) rather than by the demand (thorough analysis of the needs from the targeted population).

-   Simply be replicated from one year to another and just adjusted on the margin years after years.

-   Reflect the internal game power within a team, rather than the reality of the needs or the preference of persons of concerns.

[Quadratic voting](https://www.radicalxchange.org/media/papers/The_Handbook_for_Radical_Local_Democracy.pdf#page=6) is a cross between a voting budget system and a one-person-one-vote system. It is an innovative collective decision-making procedure where individuals allocate votes to express the degree of their preferences, rather than just the direction of their preferences. The procedure is designed to address inherent challenges associated with approaches based on either the "one-person-one-vote" or "one-dollar-one-vote" method, i.e.:

-   [Voting paradox](https://en.wikipedia.org/wiki/Paradox_of_voting) when majority wishes enter in conflict with each other.

-   [Tyranny of the majority](https://en.wikipedia.org/wiki/Tyranny_of_the_majority) in which a league of individuals may pursues exclusively its own objectives at the expense of those of other minorities in the group.

Quadratic voting is therefore effective at enabling optimal consensus while limiting opinions polarization.



## Deliberate & vote: mainstreaming participatory budgeting internally and externally

Many areas have been proposed for quadratic voting, including not only allocating budgets but also corporate governance in the private sector, cost-benefit analyses for public goods, more accurate polling, and other democratic decisions. For instance, quadratic voting was conducted in an experiment by the Democratic caucus of the Colorado House of Representatives in April 2019. Lawmakers used it to decide on their legislative priorities for the coming two years, selecting among 107 possible bills.

Quadratic voting can be used by UNHCR to adopt [participatory budgeting](https://www.participatorybudgeting.org/what-is-pb/), a process that allow an effective participation of persons in concerns in the definition of supporting activities, which is de facto an effective way to enforce the [Accountability to Affected people (AAP) guidance](https://www.unhcr.org/handbooks/aap/documents/UNHCR-AAP_Operational_Guidance.pdf#page=17):

> "Programme decisions are informed by documented consultations with persons of concern".

In such case, in addition to the Multi Functional Teams members, the same voting questionnaire would be filled by representatives and/or randomly selected members of Forcibly Displaced People. Results from each voting assembly can be then compared to re-enforce their authoritativeness, or at least representativeness.


## How quadratic voting works?

. Then:

-   Each member has several allocated voting credits to use either "for" (use a positive number) or "against" (use a negative number) each of the proposed activities presented for voting. When an MFT member has no opinion, he will leave the activity to "0".

-   The number of voting credits is proportional to the number of activities, MFT members can vote for: 10 credits per activity but participants can re-allocate them according to the trade-off they are ready to consent for.

-   Every additional vote (whether it is "for" or "against" a specific position) cost an exponential amount of credits: the stronger one wants to express its opinion on one specific point, the less he will be able to express it on others.

-   The order in which the activities to vote for are presented is randomized (done by the software) for each participant to avoid specific ranking/selection effects in the online form.

-   Members can submit the result of the consultation only once they have allocated all their total voting credits. At the end of the questionnaire, there is a total credit count that can be checked.

After the vote, the compilation of results can be then turned into weighting measurement for each activity, which can provide objective and recordable evidence of views to inform either what statistical evidence building should be built or how the budget should be allocated between all activities in an operation.

